---
date: "2019-05-05T00:00:00+01:00"
title: "Update tidywearable"
linktitle: "2 Update tidywearable"
author: admin
type: book
weight: 2
commentable: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

## Check `tidywearable` version

You can use the `tidywearable` to check the version of all packages and update them.

If you want to check if there are updates for `tidywearable` and packages in it. Just check it like this.

```{r, echo=TRUE, eval=TRUE}
tidywearable::check_tidywearable_version()
```

This will list all the packages version and if there are some new versions can be updated.

## Update `tidywearable`

The `update_tidywearable()` function can be used to update `tidywearable` and packages within it.

```{r, echo=TRUE, eval=FALSE}
tidywearable::update_tidywearable(from = "gitlab")
```

You can change the `from` argument if `from = "gitlab"` doesn't work.

1. "github"

2. "gitee"

3. "tidywearable.org"

If all the options of `from` don't work, you can try to set `fastgit` as `TRUE`.

```{r, echo=TRUE, eval=FALSE}
tidywearable::update_tidywearable(from = "gitlab",
                          fastgit = TRUE)
```

## Session information

```{r,eval=TRUE,warning=FALSE, R.options="", message=FALSE, cache=TRUE}
sessionInfo()
```